Iterative construction of replicated designs based on Sobol' sequences

### 2016-06-13 crass/crassnew.tex
Solving conflicts changes choice vectors e_j
Revert "Merge branch 'master' of https://github.com/fjhickernell/SobolIndices"
This reverts commit cbdb7ad57a772cf1e429b2c5c10c103e85a7da9a, reversing
changes made to 5d6d73d7005a6f882b5cd52485642ae80295075b.
Revert "changes vectors e_j"
This reverts commit de9a54ecb6a39d0b851b7457804889c4fb70baf7.

Left multiplications by matrices $L$ and $L'$ in \eqref{dig.shift} and \eqref{ibinom.scrambling}  are called linear scramblings \cite{Matousek} while additions by vectors $\ve_j$ and ${\ve'}_j$ are referred as digital shifts. There are exactly $2^r$ different choices of $\ve_j$ and ${\ve'}_j$ and $2^{r(r-1)/2}$ choices of $L$ and $L'$. To guarantee that new points added will fill unexplored regions of the input space, vectors $\ve_j$ (resp. ${\ve}'_j$) are selected as follows:
\begin{itemize}
\item[i)] for the first dimension, the same vector $\ve_1=(0,\dots,0)$ (resp. ${\ve}'_1=(0,\dots,0)$) is selected at each iteration $\ell$,
\item[ii)] for the other dimensions, vectors $\ve_2,\dots,\ve_s$ (resp. ${\ve}'_2,\dots,{\ve}'_s$) are selected to guarantee that the set $\{\ve_2,\dots,\ve_s\}$ is different at each step $\ell$ and different from $\{\ve_1,\dots,\ve_1\}$. There exists exactly $2^{r (s-1)}$ combinations of this set. At each step $\ell$, one combination is sampled without replacement. 
\end{itemize}
The maximum number of iterations $\ell$ that can be performed equals the number of combinations of the set $\{\ve_2,\dots,\ve_s\}$. If this maximum is reached, designs $\mathcal{P}_\ell$ and $\mathcal{P}'_\ell$ both correspond to a full grid design of $2^{rs}$ points.
%We have the following result:
%\item[Step 4.] The two blocks $B_l$ and ${B'}_l$ are then both randomized using the same Owen's scrambling column-wise.

@@

We name by design $A$ (resp. $B$) one of the two replicated designs constructed with the multiplicative (resp. additive) approach. We set the input space dimension $s$ to $6$. Design $A$ is refined until $\ell=12$, and design $B$ is constructed with an initial value $r=8$ and refined 15 times.  We construct $100$ designs $A$ and $B$ whose average criteria are presented in Figure \ref{results.crit}. Each of the $100$ designs $A$ is independently randomized by applying Owen's scrambling. Each of the $100$ designs $B$ is constructed by randomly selecting the matrix $L$ among the $2^{r(r-1)/2}$ choices and by selecting the vectors $\ve_j$ following steps i) and ii). We also represent  in Figure \ref{results.crit} the results obtained with a Latin Hypercube design with an equal number of points of design $B$. The x-axis corresponds to the number of points N of the design. The y-axis corresponds to the value of the criterion. A logarithmic scale is used for both axis.

>>>>

Left multiplications by matrices $L$ and $L'$ in \eqref{dig.shift} and \eqref{ibinom.scrambling}  are called linear scramblings \cite{Matousek} while additions by vectors $\ve_j$ and ${\ve'}_j$ are referred as digital shifts. There are exactly $2^r$ different choices of $\ve_j$ and ${\ve'}_j$ and $2^{r(r-1)/2}$ choices of $L$ and $L'$. To guarantee that new points added will fill unexplored regions of the input space, vectors $\ve_j$ (resp. ${\ve}'_j$) are selected as follows:
\begin{itemize}
\item[i)] for the first dimension, the same vector $\ve_1$ (resp. ${\ve}'_1$) is selected at each iteration $\ell$,
\item[ii)] for the other dimensions, vectors $\ve_2,\dots,\ve_s$ (resp. ${\ve}'_2,\dots,{\ve}'_s$) are selected to guarantee that the set $\{\ve_2,\dots,\ve_s\}$ is different at each step $\ell$. There exists exactly $2^{r (s-1)}$ combinations of this set. At each step $\ell$, one combination is sampled without replacement. 
\end{itemize}
The maximum number of iterations $\ell$ that can be performed equals the number of combinations of the set $\{\ve_2,\dots,\ve_s\}$. If this maximum is reached, designs $\mathcal{P}_\ell$ and $\mathcal{P}'_\ell$ both correspond to a full grid design of $2^{rs}$ points.
%We have the following result:
%\item[Step 4.] The two blocks $B_l$ and ${B'}_l$ are then both randomized using the same Owen's scrambling column-wise.

@@

We name by design $A$ (resp. $B$) one of the two replicated designs constructed with the multiplicative (resp. additive) approach. We set the input space dimension $s$ to $6$. Design $A$ is refined until $\ell=12$, and design $B$ is constructed with an initial value $r=8$ and refined 15 times.  We construct $100$ designs $A$ and $B$ whose average criteria are presented in Figure \ref{results.crit}. Each of the $100$ designs $A$ is independently randomized by applying Owen's scrambling. Each of the $100$ designs $B$ is constructed by randomly selecting the matrix $L$ among the $2^{r(r-1)/2}$ choices and by selecting the vectors $\ve_j$ following steps i) and ii). We also represent  in Figure \ref{results.crit} the results obtained with a Latin Hypercube design with an equal number of points of design $B$. The x-axis corresponds to the number of points $N$ of the design. The y-axis corresponds to the value of the criterion. A logarithmic scale is used for both axis.
